---
output: github_document
---


```{r, include=FALSE}
if (requireNamespace("git2r")) {
  repo = git2r::repository(".")
  url = git2r::remote_url(repo, remote = "origin") 
  gh_user = basename(dirname(url))
} else {
  gh_user = "simonvandekar"
}
```

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/`r gh_user`/pbj?branch=master&svg=true)](https://ci.appveyor.com/project/`r gh_user`/pbj)
[![Travis build status](https://travis-ci.com/`r gh_user`/pbj.svg?branch=master)](https://travis-ci.com/`r gh_user`/pbj)  

  
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pbj

The pbj package includes a set of parametric bootstrap joint (PBJ)
    testing procedures designed for neuroimaging data. The statistical tools
    are more generally applicable, but this package is designed to allow input
    and output data for NIfTI images. The PBJ tools are designed for voxel-wise
    and cluster-extent hypothesis testing methods and include semi-PBJ (sPBJ)
    inference that is robust to variance misspecification using an estimating
    equations approach.

## Installation

You can install the released version of pbj from GitHub:

``` r
devtools::install_github("simonvandekar/pbj")
```
